Analyzing Toronto Island Ferry Ticket Counts

### 2024-09-25 outputs/paper/paper.qmd
changed folder summary

#### Loading the Cleaned Dataset ####
marriage_licence_packages <- search_packages("Toronto Island Ferry Ticket Counts")
marriage_licence_packages
# Retrieve a list of all resources (datasets) available within the found package
marriage_licence_resources <- marriage_licence_packages %>%
  list_package_resources()
# Display the list of resources available in the "Marriage Licence Statistics" package
marriage_licence_resources
marriage_licence_statistics <- marriage_licence_resources[2,] %>%
  get_resource()
dir.create(here::here("outputs"), showWarnings = FALSE)
dir.create(here::here("outputs/data"), showWarnings = FALSE)

# Save the retrieved dataset to a CSV file
write_csv(marriage_licence_statistics, here::here("outputs/data/a.csv"))
data=marriage_licence_statistics
data <- read_csv(here::here("outputs/data/a.csv"))

@@

ggplot(data, aes(x = Timestamp)) +
  geom_line(aes(y = Redemption.Count, color = "Redemption Count")) +
  geom_line(aes(y = Sales.Count, color = "Sales Count")) +
  labs(title = "Redemption and Sales Counts Over Time",
       x = "Time",
       y = "Count") +
  scale_color_manual(name = "Legend", values = c("Redemption Count" = "blue", "Sales Count" = "red")) +
  theme_minimal()
```

@@

The plot reveals significant variations in ferry usage over time. We observe several peaks in both redemption and sales counts, likely aligning with periods of high activity, such as weekends, holidays, or the peak tourist season during the summer months. These spikes suggest increased demand during favorable weather or event-driven occasions. Conversely, the noticeable dips in the graph may correspond to regular weekdays or off-season times, indicating lower ferry usage during these periods. This information is valuable for understanding the temporal dynamics of ferry operations and can inform better resource management and scheduling.
\newpage

@@

ggplot(data, aes(x = Redemption.Count, y = Sales.Count)) +
  geom_point(color = "purple", size = 3) +
  labs(title = "Scatter Plot of Redemption vs Sales Count",
       x = "Redemption Count",
       y = "Sales Count") +
  theme_minimal()
```

>>>>

#### Loading the Cleaned Dataset ####
marriage_licence_packages <- search_packages("Toronto Island Ferry Ticket Counts")
marriage_licence_resources <- marriage_licence_packages %>%
  list_package_resources()

# Retrieve the dataset
marriage_licence_statistics <- marriage_licence_resources[2,] %>%
  get_resource()

# Create necessary directories
dir.create(here::here("STA304/paper1/ferrySale/outputs"), showWarnings = FALSE, recursive = TRUE)

# Save the dataset to a CSV file
write_csv(marriage_licence_statistics, here::here("STA304/paper1/ferrySale/outputs/a.csv"))

# Read the dataset back
data <- read_csv(here::here("STA304/paper1/ferrySale/outputs/a.csv"))

@@

# Plot Redemption and Sales Counts Over Time
ggplot(data, aes(x = `Timestamp`)) +
  geom_line(aes(y = `Redemption.Count`, color = "Redemption Count")) +
  geom_line(aes(y = `Sales.Count`, color = "Sales Count")) +
  labs(title = "Redemption and Sales Counts Over Time",
       x = "Time",
       y = "Count") +
  scale_color_manual(name = "Legend", values = c("Redemption Count" = "blue", "Sales Count" = "red")) +
  theme_minimal()
```

@@

The plot reveals significant variations in ferry usage over time. We observe several peaks in both redemption and sales counts, likely aligning with periods of high activity, such as weekends, holidays, or the peak tourist season during the summer months. These spikes suggest increased demand during favorable weather or event-driven occasions. Conversely, the noticeable dips in the graph may correspond to regular weekdays or off-season times, indicating lower ferry usage during these periods. This information is valuable for understanding the temporal dynamics of ferry operations and can inform better resource management and scheduling.

@@

ggplot(data, aes(x = Redemption.Count, y = Sales.Count)) +
  geom_point(color = "purple", size = 3, alpha = 0.7) +  # Add transparency for overlapping points
  labs(title = "Relationship Between Redemption and Sales Count",
       subtitle = "Scatter plot with Redemption Count on X-axis and Sales Count on Y-axis",
       x = "Redemption Count (units)",
       y = "Sales Count (units)",
       caption = "Source: Company Sales Data") +  # Add a caption for clarity
  theme_minimal(base_size = 14) +  # Increase base font size for readability
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),  # Center and bold the title
    plot.subtitle = element_text(hjust = 0.5),  # Center the subtitle
    axis.title.x = element_text(face = "italic", margin = margin(t = 10)),  # Italicize X axis label and add margin
    axis.title.y = element_text(face = "italic", margin = margin(r = 10)),  # Italicize Y axis label and add margin
    panel.grid.major = element_line(color = "gray80", size = 0.5),  # Make grid lines more subtle
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    plot.caption = element_text(hjust = 1, face = "italic", color = "gray40")  # Style caption
  )
